The limits of self commitment and private paternalism \thanks{}

### 2022-04-28 OA.tex
Fan & Park Bounds

 Recall that $Z_i$ is the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the forced-fee arm, and $Z_i=2$ is the choice arm.  Let $C_i$ be the unobserved choice type. $C_i=0$ when individual $i$ does not choose commitment  given the choice and $C_i=1$ when chooses commitment given the choice. Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + T_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.

@@

>>>>

 Recall that $Z_i$ is the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the forced-fee arm, and $Z_i=2$ is the choice arm.  Let $C_i$ be the unobserved choice type. $C_i=0$ when individual $i$ does not choose commitment  given the choice and $C_i=1$ when chooses commitment given the choice. Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + C_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.

@@

\begin{table}[H]
\caption{Effect of frequent payment in observational data}
\label{attrition_table}
\begin{center}
\scriptsize{\input{./Tables/def_te_obs.tex}}
\end{center}
 \scriptsize 
%\textit{Do file: } \texttt{def\_te\_obs.do}
\end{table}

### 2022-04-28 donde.tex
Fan & Park Bounds

    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{\% better when forced to Hard commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}

@@

>>>>

    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \caption{\% better when forced to forced commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}

@@

\begin{figure}[H]
        \caption{Learning over time}
    \label{fc_discount_rates}
    \begin{center}
        \centering
        \includegraphics[width=0.55\textwidth]{Figuras/learning_over_time.pdf}
    \end{center}
     \scriptsize This Figure shows the evolution of default over time as borrowers have more options to choose the frequent payment contract. This uses the observational data. 
     %\textit{Do file: }  \texttt{learning\_over\_time.do}
\end{figure}
